---
title: "Submission1-HW3"
subtitle: "Research Methods, Spring 2024"
author: "Caroline Hansen"
format:
  pdf:
    output-file: "carolinehw3-1"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---

https://github.com/carolinezhansen/tobacco/tree/main

```{r}
#| include: false
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra)
```

```{r}
#| include: false
#| eval: true

load("Hwk3_workspace.Rdata")
```



# Answers for Homework 3: Submission 1
\newpage

# Problem 1 
\noindent 1. Present a bar graph showing the proportion of states with a change in their cigarette tax in each year from 1970 to 1985.
```{r} 
#| echo: false
#| label: bar
#| fig-cap: "Proportion of States with a Tax Change per Year"

graph1
```
\newpage
# Problem 2 
\noindent 2. Plot on a single graph the average tax (in 2012 dollars) on cigarettes and the average price of a pack of cigarettes from 1970 to 2018.
```{r} 
#| echo: false
#| label: graph2
#| fig-cap: "Average Tax and Average Price of Cigarettes from 1970 to 2018"

graph2
```

\newpage
# Problem 3
\noindent 3. Identify the 5 states with the highest increases in cigarette prices (in dollars) over the time period. Plot the average number of packs sold per capita for those states from 1970 to 2018.
```{r}
#| echo: false
#| label: problem3
#| fig-cap: "Average Packs Sold per Capita for Top 5 States with Highest Price Increases"

graph3
```

\newpage
# Problem 4
\noindent 4. Identify the 5 states with the highest increases in cigarette prices (in dollars) over the time period. Plot the average number of packs sold per capita for those states from 1970 to 2018.
```{r}
#| echo: false
#| label: problem4
#| fig-cap: "Average Packs Sold per Capita for Bottom 5 States with Lowest Price Increases"

graph4
```

\newpage
# Problem 5
\noindent 5. Identify the 5 states with the highest increases in cigarette prices (in dollars) over the time period. Plot the average number of packs sold per capita for those states from 1970 to 2018.
```{r}
#| echo: false
#| label: problem5
#| fig-cap: "Comparison of Sales Trends between High and Low Price Increase States"

compareincreases
```